Dynamical modeling of tidal streams

### 2014-01-02 tex/ms.tex
streams: add reference to discussion section

First, we compute the distribution of $\Delta \opar$, the frequency
offset between stream members and the progenitor given the angle
offset $\Delta \apar$ as follows (considering $\Delta \opar$ to be
positive)
\begin{equation}\label{eq:poparapargeneral}
\begin{split}
  p(\Delta \opar|\Delta \apar) & = \int \dd \ts\,p(\Delta \opar,\ts|\Delta \apar)\, \\
  & \propto \int \dd \ts \,p(\Delta \apar | \Delta \opar,\ts)\,p(\Delta \opar,\ts)\,,\\
  & \approx \int \dd \ts \,\delta(\Delta \apar - \Delta \opar\,\ts)\,p(\Delta \opar,\ts)\,,\\
  & = \frac{1}{\Delta \opar}\,p(\Delta \opar,\frac{\Delta \apar}{\Delta \opar})\,,
\end{split}
\end{equation}
where in the penultimate step we have approximated the initial angle
distribution as a delta function (as the initial angle offset is small
with respect to the final offset). This is a fully general
expression. For the fiducial stream model, this can be simplified to
\begin{equation}\label{eq:poparapar}
\begin{split}
  p(\Delta \opar|\Delta \apar) \propto &\ \frac{1}{\Delta \opar}\,p(\Delta \opar)\,,\qquad 0 < \frac{\Delta \apar}{\Delta \opar} < t_d\,.\\
  & 0\,,\qquad \mathrm{otherwise}\,.
\end{split}
\end{equation}
\Eqnname~(\ref{eq:poparapar}) shows why we chose to model
$p(\Delta \opar)$ as a Gaussian multiplied with $|\Delta
\opar|$. $p(\Delta \opar|\Delta \apar)$ is then a Gaussian with mean
$\Delta \Omega^m$ and variance $\sigma^2_{\Omega,1}$, for $\Delta
\opar > \Delta \apar / t_d$, and zero otherwise. The mean and variance
of such a Gaussian is straightforward to calculate in terms of error
functions. The top left panel of \figurename~\ref{fig:gd1_apar} shows
the distribution of $|\Delta \opar|$ versus $|\Delta \apar|$ (absolute
value in order to show the trailing and leading stream together) for
the simulated stream, as well as the mean and dispersion calculated
from the fiducial model. The dashed line shows $\Delta \apar = \Delta
\Omega^m \,t_d$, approximately the angle where the finite disruption
time starts to influence the mean $\Delta \opar$ of the stream. The
finite disruption time, $\approx 4.5\Gyr$ in this case, of a tidal
stream means that for stream members to have reached very large angle
differences with respect to the progenitor, they must have been
removed at large frequency differences. Around $\Delta \Omega^m
\,t_d$, average stream stars, \ie, those removed with the average
frequency offset, do not have a large enough offset to reach large
angle offsets. Therefore, even though the average frequency offset
does not change over time (see \figurename~\ref{fig:gd1_times}), the
average frequency offset, and therefore the average orbit, does change
with distance from the progenitor. It is in this sense that streams do
not follow a single orbit. This is discussed further in BOVY:REF.

@@

\subsection{Do streams follow orbits?}

>>>>

First, we compute the distribution of $\Delta \opar$, the frequency
offset between stream members and the progenitor given the angle
offset $\Delta \apar$ as follows (considering $\Delta \opar$ to be
positive)
\begin{equation}\label{eq:poparapargeneral}
\begin{split}
  p(\Delta \opar|\Delta \apar) & = \int \dd \ts\,p(\Delta \opar,\ts|\Delta \apar)\, \\
  & \propto \int \dd \ts \,p(\Delta \apar | \Delta \opar,\ts)\,p(\Delta \opar,\ts)\,,\\
  & \approx \int \dd \ts \,\delta(\Delta \apar - \Delta \opar\,\ts)\,p(\Delta \opar,\ts)\,,\\
  & = \frac{1}{\Delta \opar}\,p(\Delta \opar,\frac{\Delta \apar}{\Delta \opar})\,,
\end{split}
\end{equation}
where in the penultimate step we have approximated the initial angle
distribution as a delta function (as the initial angle offset is small
with respect to the final offset). This is a fully general
expression. For the fiducial stream model, this can be simplified to
\begin{equation}\label{eq:poparapar}
\begin{split}
  p(\Delta \opar|\Delta \apar) \propto &\ \frac{1}{\Delta \opar}\,p(\Delta \opar)\,,\qquad 0 < \frac{\Delta \apar}{\Delta \opar} < t_d\,.\\
  & 0\,,\qquad \mathrm{otherwise}\,.
\end{split}
\end{equation}
\Eqnname~(\ref{eq:poparapar}) shows why we chose to model $p(\Delta
\opar)$ as a Gaussian multiplied with $|\Delta \opar|$. $p(\Delta
\opar|\Delta \apar)$ is then a Gaussian with mean $\Delta \Omega^m$
and variance $\sigma^2_{\Omega,1}$, for $\Delta \opar > \Delta \apar /
t_d$, and zero otherwise. The mean and variance of such a Gaussian is
straightforward to calculate in terms of error functions. The top left
panel of \figurename~\ref{fig:gd1_apar} shows the distribution of
$|\Delta \opar|$ versus $|\Delta \apar|$ (absolute value in order to
show the trailing and leading stream together) for the simulated
stream, as well as the mean and dispersion calculated from the
fiducial model. The dashed line shows $\Delta \apar = \Delta \Omega^m
\,t_d$, approximately the angle where the finite disruption time
starts to influence the mean $\Delta \opar$ of the stream. The finite
disruption time, $\approx 4.5\Gyr$ in this case, of a tidal stream
means that for stream members to have reached very large angle
differences with respect to the progenitor, they must have been
removed at large frequency differences. Around $\Delta \Omega^m
\,t_d$, average stream stars, \ie, those removed with the average
frequency offset, do not have a large enough offset to reach large
angle offsets. Therefore, even though the average frequency offset
does not change over time (see \figurename~\ref{fig:gd1_times}), the
average frequency offset, and therefore the average orbit, does change
with distance from the progenitor. It is in this sense that streams do
not follow a single orbit. This is discussed further in
\sectionname~\ref{sec:discussorbit}.

@@

\subsection{Do streams follow orbits?}\label{sec:discussorbit}
